Beyond Adaptive Web Design

### 2014-03-18 paper/paper.tex
feat: gyroscope rotation experiment
feat: voice commands experiment
refactor: google glass description

Web browsers on TVs are actually really good but the input is terrible so no one uses them. Input is much more important to interface design than screen size. The input defines what a design needs to do in order to accomplish a task~\cite{adaptiveinput}. We also have wearable computers. The current Google Glass interface is limited to a floating display above head. We do not have full range of motion and, as a result, no spatial cues or depth in the interface.

@@

We have created an experiment based on our module which provides control over to-do list. There were 7 voice commands using exact expressions and 9 using regular expressions. But there are much more interesting things we can achieve using speech input. We can even use multiple languages for speech recognition. One of the biggest problems of the voice commands is however incorrect speech recognition. To solve this issue we can conditionalize regular expressions or use utterance error correction.

@@

\noindent However some problems have been detected. The biggest one is that browser vendors do not use specification correctly and use own orientation ranges and directions. This causes some scroll issues.

>>>>

Web browsers on TVs are actually really good but the input is terrible so no one uses them. Input is much more important to interface design than screen size. The input defines what a design needs to do in order to accomplish a task~\cite{adaptiveinput}. We also have wearable computers. The current Google Glass interface is also limited to several input methods.

@@

We have created an experiment based on our module which provides control over to-do list. There were 7 voice commands using exact expressions and 9 using regular expressions. This has been the most popular input method and the experiment has been attended by thousands of users. But there are much more interesting things we can achieve using speech input. We can even use multiple languages for speech recognition. One of the biggest problems of the voice commands is however incorrect speech recognition. To solve this issue we can conditionalize regular expressions or use utterance error correction.

@@

\noindent The experiment has been attended by thousands of users. However some problems have been detected. The biggest one is that browser vendors do not use specification correctly and use own orientation ranges and directions. This causes some scroll issues.
